Summary of cell type ontologies in reference files

### 2025-08-25 analyses/cell-type-consensus/exploratory-notebooks/06-update-consensus-scimilarity.Rmd

@@

Generally speaking it looks like there are terms that are of the same lineage which makes sense. 
I think we could just stick with our previous guidelines of choosing the label with the fewest descendants or is the most specific term.

>>>>

It looks like we have ~7500 cases where there is more than one unique LCA identified. 
What are the possible LCAs for those scenarios?

@@

Generally speaking it looks like there are terms that are of the same lineage which makes sense. 
I think we could just stick with our previous guidelines of choosing the label with the fewest descendants or the most specific term.
